### 2023-11-22 README.Rmd
update readme

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/StewartWILDlab/rofcamtrap/main?urlpath=rstudio)

@@

@@

```
for FILE in project*
    mdtools postprocess --write-csv $FILE
end
```

>>>>

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/StewartWILDlab/rofcamtrap/main?urlpath=rstudio) -->

@@

9. Crop annotations.

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/2_LabelStudio/0_inputs/TrailCamStorage_2" \
  crop
```

## Label studio outputs

1. Enter the container running the label studio app and output ths number of projects

```{bash eval=FALSE}
docker exec -it label-studio-app-1 bash
curl -X GET http://localhost:8080/api/projects/ -H 'Authorization: Token 3135fdd1f4a5b9b3630b69011ec4d70e7800c41d' -o files/outputs/project_counts.json
```

2. On the instance outside the container, run the Python script to extract projects id

```{python eval=FALSE, python.reticulate = FALSE}
import json

with open('data/outputs/project_counts.json', 'r') as file:
  data = json.load(file)

ids = [data['results'][i]['id'] for i in range(len(data['results']))]

with open('data/outputs/project_ids.txt', 'w') as file:
  for the_id in ids:
        file.write(str(the_id) + '\n')
```

3. Back in the container

```{bash eval=FALSE}
arr=(170 86 85 84 83 82 81 80 79 78 77 76 75 74 73 72 65 64 63 62 61 60 59 58 57 55 54 53 52 51 50 49 48 47 46 44 43 42 41 40 39 37 35 33 32 31 30 28 25 23 21 20 19 18 17 16 15 13 10); 
for id in ${arr[@]}; do         
  # url="http://localhost:8080/api/projects/${id}/export?exportType=JSON&download_all_tasks=true";
  url="http://localhost:8080/api/projects/${id}/export?exportType=JSON";
  curl -X GET "$url" -H 'Authorization: Token 3135fdd1f4a5b9b3630b69011ec4d70e7800c41d'\
    -o "files/outputs/ls/output_file_$id.json";
done
```

4. Check for file numbers

```{bash eval=FALSE}
ls data/outputs/ls # 59 nov 21
```

5. Copy to local machine

```{bash eval=FALSE}
scp -i ssh_key/arbutus_def_fstewart_prod 'ubuntu@206.12.94.17:~/data/outputs/ls/*' rofcamtrap/2_LabelStudio/1_outputs_downloaded/
```

6. Process those outputs

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -i "/workspace/rofcamtrap/2_LabelStudio/1_outputs_downloaded/" \
  -o "/workspace/rofcamtrap/2_LabelStudio/2_outputs_processed" \
  post
```

@@

```{bash eval=FALSE}
for FILE in project*
    mdtools postprocess --write-csv $FILE
end
```
